An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-17 main.tex
Conclusion paragraph

% There are various areas for further work to build on this. Firstly, an analysis
% of the effect of noise would offer insights about the stability of the findings.
% It would also be possible to consider three or more types of strategy in the
% population and finally mutation would also offer an interesting dimension to
% explore.

>>>>

There are many opportunities build on this work. In particular, an analysis
of the effect of noise should offer insights regarding the stability of the findings,
particularly for the handshaking strategies. They may be less dominant for
larger amounts of noise since the handshaking mechanisms may become brittle.
There are many other variations to explore including populations with more
than one type, spatial structure, and mutation.
